---
title: "R Ladies Nairobi Shiny Exercise guide"
author: "Dorcas K"
date: "12/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

As good coding habit, always write down at the top of the script detais that can help someone else suing the code.

1. We use the ui.R script

SO the first few lines (commented), add the details of this exercise. Author name, Date (exact or month), and purpose of the script.

```{r details of script}
#Dorcas Kareithi
#December 2020
#Task: Create a Shiny App to explore the reach of Nairobi R ladies in twitter
```


After that, we load all the libraries we may need

```{r loading libraries}
library(shiny)
library(ggplot2)
library(plyr)
library(dplyr)
library(shinyWidgets)
library(RColorBrewer)
library(plotly)
library(leaflet)
library(readxl)
library(shinythemes)

#We may need to install one more library (changed the dataset last minute when I found out that Twotter is blocked in the country I am currently at and wanted to do a live dashboard)
#Installing the tidy covid 19 package

#Install tidycovid package. Uncomment the line below
#remotes::install_github("joachim-gassen/tidycovid19")

#once done installing, comment back and load the libraries below

library(tidycovid19)
library(tidyverse)

```


```{r data preparation}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
